{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2024-12-22 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

    Fix any arbitrary $y \in \RR^n$, define for all $x \in Q$: 

@@

    and the proximal gradient operator $T_L := [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f]$. 

@@

        T_Ly = \argmin_x \left\lbrace

@@

        \right\rbrace. 
    It is a single-valued mapping, and it has its domain on the entire $\RR^n$. 
    Another operator often associated with $T_L$ is the gradient mapping operator $\mathcal G_L:= L(I - T_L)$. 

@@

    The lemma follows explains equates between $\mathcal M(\cdot; y), \widetilde{\mathcal M}(\cdot; y)$. 

@@

        Fix any $y \in \RR^n$, we will have for all $x \in Q$ that: 

@@

@@

@@

    \subsection{Proximal inequality}

@@

        Fix any $y\in \RR^n$, we have for all $x \in Q$: 
            - L\Vert y - T_L y\Vert^2
        When $f$ is $\mu \ge 0$ strongly convex, it implies that 

@@

        Observe that the function $\widetilde {\mathcal M}(\cdot; y)$ is $L$ strongly convex with minimizer $T_Ly$. 
        For all $x \in Q$, it has quadratic growth condition at its minimizer $T_Ly$ which gives these equivalent inequalities: 

@@

            \widetilde{\mathcal M}^{L^{-1}}(T_Ly; y)

@@

            \frac{L}{2}\Vert x - T_Ly\Vert^2

@@

            \mathcal M^{L^{-1}}(T_Ly; y) 

@@

            \frac{L}{2}\Vert x - T_Ly\Vert^2

@@

            - \frac{L}{2}\Vert x - T_Ly\Vert^2

@@

                F(x) - F(T_Ly) 

@@

                \frac{L}{2}\Vert T_Ly - y\Vert^2

@@

            - \frac{L}{2}\Vert x - T_Ly\Vert^2

@@

                    \Vert x - T_Ly + T_Ly - y\Vert^2
                    \Vert y - T_Ly\Vert^2
            - \frac{L}{2}\Vert x - T_Ly\Vert^2

@@

                F(x) - F(T_Ly) 
                    \Vert x - T_Ly\Vert^2 + 
                    2\langle x - T_Ly, T_Ly - y\rangle
            - \frac{L}{2}\Vert x - T_Ly\Vert^2

@@

                F(x) - F(T_Ly) + \frac{L}{2}\Vert x - T_Ly\Vert^2 
                - L\langle  x - T_Ly, y - T_Ly\rangle
            - \frac{L}{2}\Vert x - T_Ly\Vert^2
            F(x) - F(T_Ly)
            - \langle L(y - T_Ly), x - T_Ly\rangle

@@

@@

        The first $\implies$ comes from Lemma \ref{lemma:pg-envelope} where we had $- \widetilde{\mathcal M}^{L^{-1}}(x; y) \ge - \mathcal M^{L^{-1}}(x; y)$. 
        \todoinline{THIS THIS PART IS WRONG WRONG WRONG!}. 
        Continuing, it has: 
            F(x) - F(T_Ly) - \langle L(y - T_Ly), x - T_Ly\rangle - D_f(x, y) &\ge 0
            F(x) - F(T_Ly)
            - \langle L(y - T_Ly), x - y + y - T_Ly\rangle - D_f(x, y) 
            F(x) - F(T_Ly)
            - \langle L(y - T_Ly),x - y \rangle
            - L\Vert y - T_Ly\Vert^2

@@

            F(x) - F(T_Ly)
            - \langle L(y - T_Ly),x - y \rangle
            - \frac{L}{2}\Vert y - T_Ly\Vert^2
            F(x) - F(T_Ly)
            - \langle L(y - T_Ly),x - y \rangle
            - \frac{L}{2}\Vert y - T_Ly\Vert^2

@@

        Going from the second last inequality to the last inequality, we used the fact that $f$ is strongly convex hence for all $x, y$, it's true that $D_f(x, y) \ge \mu/2 \Vert x - y\Vert^2$. 

>>>>

    Fix any arbitrary $y \in \RR^n$, define the model functions for all $x \in Q$

@@

    When $x \in \RR\setminus Q$, the model function takes $+\infty$ value. 
    Define the proximal gradient operator and gradient mapping operator:  $T_L := [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f]$. 

@@

        T_Ly &= \argmin_x \left\lbrace

@@

        \right\rbrace,
        \mathcal G_L 
        &:= L(I - T_L). 
    $T_L$ is a single-valued mapping, and it has its domain on the entire $\RR^n$. 

@@

    The following lemma is an important property of $\mathcal M(\cdot; y), \widetilde{\mathcal M}(\cdot; y)$. 

@@

        Fix any $y \in \RR^n$, we will have for all $x \in \RR$ that: 

@@

        Consider any $x \in Q$, by definition it has: 

@@

        The equality is trivially true when $x \in \RR \setminus Q$. 

@@

        This is true not just for fixed $L$ that is the Lipschitz smoothness constant of $f$, it's true for all value of $L$. 

@@

        Fix any $y\in \RR^n$, we have for all $x \in \RR^n$: 

@@

        We denote $T$ for the proximal gradient operator instead of $T_L$. 
        We can do this because the Lipschitz constant $L$ is fixed throughout the proof hence it can be omitted. 
        The model function $\widetilde{\mathcal M}^{L^{-1}}(\cdot; y)$ is a $L$ strongly convex function, so it admites quadratic growth conditions over minimizer $Ty$ and for all $x \in \RR^n$: 
        {\footnotesize

@@

            \widetilde{\mathcal M}^{L^{-1}}(Ty; y)

@@

            \frac{L}{2}\Vert x - Ty\Vert^2

@@

            \mathcal M^{L^{-1}}(Ty; y) 

@@

            \frac{L}{2}\Vert x - Ty\Vert^2
            + D_f(Ty; y)

@@

            - \frac{L}{2}\Vert x - Ty\Vert^2
            + D_f(Ty; y)

@@

                F(x) - F(Ty) 

@@

                \frac{L}{2}\Vert Ty - y\Vert^2
            + D_f(Ty; y)
            - \frac{L}{2}\Vert x - Ty\Vert^2
                F(x) - F(Ty) 
                    \Vert x - Ty + Ty - y\Vert^2

@@

                    \Vert y - Ty\Vert^2
            + D_f(Ty; y)
            - \frac{L}{2}\Vert x - Ty\Vert^2

@@

                    \Vert x - Ty\Vert^2 + 
                    2\langle x - Ty, Ty - y\rangle
            + D_f(Ty; y)
            - \frac{L}{2}\Vert x - Ty\Vert^2

@@

                F(x) - F(Ty) + \frac{L}{2}\Vert x - Ty\Vert^2 
                - L\langle  x - Ty, y - Ty\rangle
            + D_f(Ty; y)
            - \frac{L}{2}\Vert x - Ty\Vert^2

@@

            F(x) - F(Ty)
            - \langle L(y - Ty), x - Ty\rangle

@@

            + D_f(Ty, y)

@@

        Now, consider the lower bound of $D_f(x, y) \ge \mu/2\Vert x - y\Vert^2$ by strong convexity of $f$ then 
            0 &\le 
            F(x) - F(Ty)
            - \langle L(y - Ty), x - Ty\rangle

@@

            + D_f(Ty, y)
            F(x) - F(Ty)
            - \langle L(y - Ty), x - Ty\rangle

@@

            + \frac{L}{2}\Vert y - Ty\Vert^2
            F(x) - F(Ty)
            - \langle L(y - Ty), x - y  + y - Ty\rangle
            + \frac{L}{2}\Vert y - Ty\Vert^2
            F(x) - F(Ty) - \langle L(y - Ty), x - y\rangle - \frac{\mu}{2}\Vert x - y \Vert^2
            - \frac{L}{2}\Vert y - Ty\Vert^2. 
        The proof is done. 
